Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-22 doc/asplos13/relatedwork.tex
more related work, on SDSMs, gasnet

dsm, pgas
lightweight threading
other graph solutions: 
-graph parallel, distributed
--pregel - but is synchronous and thus inefficient
--graphlab - asynchrounous, esp useful for problems that have been shown empirically to converge faster with asynchrony

@@

\subsection{systems?}
RAMCloud - low latency; RPC call communication abstraction

sDSM - most are page based and deal with maintaining consistency of data; built on shared memory programming models rather than something more PGAS. They can use prefetching, based on prediction to overlap communication and computation, but does this work for irregular apps? Difference from txDSM is that we don't try to provide txns over multiple nodes, only within one core's memory.

software threads

@@

>>>>

@@

software threads
lightweight threading

RAMCloud takes a different approach and argues for optimizing networked systems for very low latency with the motivation of getting good performance regardless of access pattern, as well as reducing latency of recovery to reduce backup storage costs.

\subsection{Distribute Shared Memory}

Grappa includes a software distributed shared memory (SDSM). Many traditional SDSM systems are page based [Treadmarks,...], and a lot of work deals with maintaining consistency of data efficiently and optimizing for sharing. Grappa's shared memory is implemented by Active Messages and there is no caching under the hood. Every piece of memory in the shared address space belongs to a single core, and data can be accessed incoherently at any granularity. Grappa provides an API for explicit incoherent caching to take advantage of locality where it exists, as well as sharing.

Shared memory systems often try to reduce the cost of memory access by predicting good prefetches to overlap memory access and computation; however, this is less effective for irregular applications with fine-grained, data-dependent memory accesses. Grappa depends on high amounts of concurrency to tolerate latency with multithreading.

SDSM systems are usually built to be programmed with flat shared memory programming models like OpenMP, rather than models that make locality explicit like PGAS.

GASNet is a networking library for supporting portable implmentations of global address space applications or languages, like UPC and recently Chapel...
Grappa currently uses GASNet for networking, but does not use gasnet's mapped shared memory segments for supporting RDMA. Rather, the global address space is implemented at a higher level using Active Messages.

RAMCloud - RPC call communication abstraction like us because it supports more flexibility,...

Difference from txDSM \cite{sdsm with txn coherence} is that we don't try to provide txns over multiple nodes, only within one core's memory.

@@

\TODO{should we mention GreenMarl and how its first distributed try is compile down to Pregel}
